Simulations of Ballot Polling Risk-Limiting Audits

### 2021-10-30 MultipleRoundSims/sections/01-intro.tex
bib file, changes to intro, reordered related work and defs

%Intro
Need motivating paragraph and two sentence summary of results here.

\subsection{Background}
In the general ballot-polling risk limiting audit (RLA), a number of ballots are drawn and tallied in what is termed a {\em round} of ballots \cite{usenix_minerva}. A statistical measure is then computed to determine whether there is sufficient evidence to declare the election outcome correct within the pre-determined risk limit. Because the decision is made after drawing a round of ballots, the audit is termed a {\em round-by-round (R2)} audit. The special case when round size is one---that is, stopping decisions are made after each ballot draw---is a {\em ballot-by-ballot (B2)} audit.

@@

\Minerva was designed for R2 audits and applies its stopping rule once for each round. Thus it does not require the tracking of ballots that SO \BRAVO does. It has been proven that \Minerva is a risk-limiting audit and requires fewer ballots to be sampled than EoR \BRAVO when an audit is performed in rounds. Computations of first-round size for a 0.9 stopping probability when the election is as announced have been computed for a wide range of margins and shown to be smaller than those for both EoR and SO \BRAVO. First round simulations of \Minerva \cite{arxiv_athena} demonstrate that its first-round properties---regarding the probabilities of stopping when the underlying election is tied and when it is as announced---are as predicted for first round sizes with stopping probability 0.9. There are no results, either theoretical or based on simulations, regarding the expected number of ballots drawn in a \Minerva audit. Further, there is no literature comparing simulations of \Minerva and EoR or SO \BRAVO, or studying the sizes of multiple-round \Minerva audits.

>>>>

%Intro
The literature contains numerous descriptions of vulnerabilities in deployed voting systems, and it is not possible to be certain that any system, however well-designed, will perform as expected in all instances. For this reason, 
{\em evidence-based elections} aim to produce trustworthy and compelling evidence of the correctness of election outcomes, enabling the detection of problems with high probability. One way to implement an evidence-based election is to use a well-curated voter-verified paper trail, compliance audits, and a rigorous tabulation audit of the election outcome, known as a risk-limiting audit (RLA). This paper provides insight into the main approach to ballot polling RLAs, the \BRAVO audit \cite{bravo}, and the newer \Minerva \cite{usenix_minerva} ballot polling RLA, through the presentation of simulation results. While some properties of the two audits may be theoretically derived, for other properties theoretical results are not available. This paper examines the number of ballots drawn over multiple rounds of both audits, and also examines the related probabilities of stopping if the election is as announced, and the maximum risk of the audit.

\subsection{Background}
This paper focuses on ballot-polling RLAs, which require a large number of ballots but do not rely on any special features of the election technology. In the general ballot-polling risk limiting audit (RLA), a number of ballots are drawn and tallied in what is termed a {\em round} of ballots \cite{usenix_minerva}. A statistical measure is then computed to determine whether there is sufficient evidence to declare the election outcome correct within the pre-determined risk limit. Because the decision is made after drawing a round of ballots, the audit is termed a {\em round-by-round (R2)} audit. The special case when round size is one---that is, stopping decisions are made after each ballot draw---is a {\em ballot-by-ballot (B2)} audit.

@@

\Minerva was designed for R2 audits and applies its stopping rule once for each round. Thus it does not require the tracking of ballots that SO \BRAVO does. It has been proven that \Minerva is a risk-limiting audit and requires fewer ballots to be sampled than EoR \BRAVO when an audit is performed in rounds. Simulations have also been presented to understand better its first round properties; these show that \Minerva also draws fewer ballots than SO \BRAVO for large first rounds. There are no results, however, either theoretical or based on simulations, regarding the expected number of ballots drawn over multiple rounds in a \Minerva audit. Further, there is no literature comparing the number of ballots drawn by \Minerva and EoR or SO \BRAVO over multiple rounds.

Both \BRAVO and \Minerva have been integrated into election audit software {\em Arlo} \cite{arlo}, and, as such, available for use in real election audits. Both have been used in real election audits. For this reason, it is very important to understand their properties over multiple rounds.

### 2021-10-30 MultipleRoundSims/sections/03-defs.tex
bib file, changes to intro, reordered related work and defs

%Definitions
Now we present relevant definitions.
We consider a two candidate plurality contest.
To begin we define an audit.
\begin{definition}
An audit $\mathcal{A}$ takes a sample $X$ as input and gives one of the 
following decisions
\begin{enumerate}
\item
$Correct$: the audit is complete
\item
$Uncertain$: continue the audit
\end{enumerate}
\end{definition}
All of the audits discussed in this paper are modeled as binary hypothesis tests.
Under the alternate hypothesis, $H_a$, the announced outcome is correct. 
That is, the true underlying ballot distribution is given by the announced ballot tallies.
Under the null hypothesis, $H_0$, the true outcome is a tie 
(or a the announced winner losing by one vote if there is an odd number of total ballots).
Now we define key attributes of an audit that we will consider while analyzing our simulations.
The risk of an audit is the probability that an audit stops when a tie has occurred.
\begin{definition}[Risk]
The risk $R$ of an audit $\mathcal{A}$ is
$$R(\mathcal{A})=\Pr[\mathcal{A}(X)=Correct \mid H_0]$$
\end{definition}
This leads us to the following simple definition of an $\alpha$-RLA.
\begin{definition}[Risk Limiting Audit ($\alpha$-RLA)]
An audit $\mathcal{A}$ is a Risk Limiting Audit with 
risk limit $\alpha$ iff 
$$R(\mathcal{A}) \le \alpha.$$
\end{definition}

It is useful to discuss the probability of an audit stopping in
some round, if the outcome is correctly announced.
\begin{definition}[Stopping Probability]
The stopping probability $S$ of an audit $\mathcal{A}$ in round $j$ is 
$$S_j(\mathcal{A})=\Pr[\mathcal{A}(X_j)=Correct \mid H_a]$$
\end{definition}
The notion of stopping probability can be useful for selecting round sizes.

>>>>

%Definitions
Now we present relevant definitions.
We consider a two candidate plurality contest.
To begin we define an audit. We assume that ballots are sampled with replacement. 
\begin{definition}
An audit $\mathcal{A}$ takes a sample $X$ as input and gives one of the 
following decisions
\begin{enumerate}
\item
$Correct$: the audit is complete
\item
$Uncertain$: continue the audit
\end{enumerate}
\end{definition}
All of the audits discussed in this paper are modeled as binary hypothesis tests.
Under the alternate hypothesis, $H_a$, the announced outcome is correct. 
That is, the true underlying ballot distribution is given by the announced ballot tallies.
Under the null hypothesis, $H_0$, the true outcome is a tie 
(or the announced winner lost by one vote, and the number of ballots is large enough that the probability of drawing a ballot for the winner is that of drawing one for the winner).
Now we define key attributes of an audit that we will consider while analyzing our simulations.
The maximum risk of an audit is the probability that an audit stops, given that the underlying election is a tie. 
\begin{definition}[Risk]
The maximum risk $R$ of an audit $\mathcal{A}$ is
$$R(\mathcal{A})=\Pr[\mathcal{A}(X)=Correct \mid H_0]$$
\end{definition}
This leads us to the following simple definition of an $\alpha$-RLA.
\begin{definition}[Risk Limiting Audit ($\alpha$-RLA)]
An audit $\mathcal{A}$ is a Risk Limiting Audit with 
risk limit $\alpha$ iff 
$$R(\mathcal{A}) \le \alpha.$$
\end{definition}

It is useful to discuss the probability of an audit stopping in
the $j^{th}$ round, given that the underlying election is as announced.
\begin{definition}[Stopping Probability]
The stopping probability $S$ of an audit $\mathcal{A}$ in round $j$ is 
$$S_j(\mathcal{A})=\Pr[\mathcal{A}(X)=Correct ~in~round~j~\land \mathcal{A}(X) \neq Correct ~previously \mid H_a]$$
\end{definition}
The notion of stopping probability can be useful for selecting round sizes.

### 2021-10-30 MultipleRoundSims/sections/04-software.tex
bib file, changes to intro, reordered related work and defs

%Software
In this section we describe the software implementing ballot polling audits, termed the R2B2 library, and the simulator software. All the software is released as open source under the MIT License.
\subsection{R2B2 Library}

The R2B2 Python library provides a framework for the exploration of round-by-round
and ballot-by-ballot RLAs. The goal in designing R2B2 is two fold:
\begin{enumerate}
    \item Provide an elegant Python library which can be easily imported and used
    in any other code base.
    \item Provide an interactive set of tools which can be utilized `out-of-the-box'
    for experimenting with and learning about risk-limiting audits.
\end{enumerate}

@@

The high-level design of R2B2 is an object-oriented view of election audits.
The three main object classes, \code{Election}, \code{Contest}, and \code{Audit},
-serve to group data into logically independent structures.

@@

The \code{Audit} contains information related to the audit parameters for a single contest, 
such as the risk limit, sampling method, and \code{Contest} to audit. It is important
to note the \code{Audit} is an Abstract Base Class upon which specific RLAs are built.
It only contains the parameters and attributes common to all RLAs and provides a set
of methods that can be called by any audit implementation. The functionality of
\code{Audit} can be divided into two basic groups: \textit{interactive}
and \textit{bulk}.\\
\\
The interactive implementation allows users to execute an audit step-by-step as it
might progress during a live election audit through the following:

@@

\subsection{Simulations to Support Theoretical Audit Properties}

The outcomes of RLAs depend on random chance; some random samples
support the alternative hypothesis more than expected, resulting in 
quick low-risk conclusions, while other samples require subsequent
rounds in order to confirm the announced results.
We can simulate random samples for various underlying ballot 
distributions by computing pseudorandom samples. 
By applying an audit's stopping condition to thousands of such
simulated samples, the average behavior of the simulated
audits will tend towards the true behavior of the audit.
In this way, we can examine whether theoretical claims about an audit are
actually correct.

\subsection{Software for Simulations}
Our open source audit software library r2b2 [link] has implementations of several ballot polling risk-limiting audits as well as a simulator, 
all written in Python.
For each of these audits, the software can evaluate the stopping condition for a given sample and can give estimates
of the minimum round size to achieve a desired stopping probability. 
For a given audit and random seed, the simulator draws random samples using the pseudorandom number generator, [need to check].
Ballots can be sampled from any distribution of the users choosing. 
It is often useful to consider the distribution of ballots corresponding to a tie and the 
distribution of ballots corresponding with the announced results; these are the distributions represented
by the null and alternative hypotheses.
After drawing a sample, the simulator then evaluates the given audit's stopping condition for this simulated sample.
If the audit stops, the simulation stops, and if the audit continues, the simulation draws another round. 
The abstract simulator class does not prescribe any one method for choosing round sizes. 
We implement several classes to support various round size choices: 
round sizes from an estimate to achieve a desired probability of stopping, 
predetermined round sizes, and random round sizes.

>>>>

%Software
In this section we describe the software implementing ballot polling audits, termed the R2B2 library, and the simulator software used for this research. All the software is released as open source under the MIT License.
\subsection{R2B2 Library}

The R2B2 Python library \cite{r2b2} provides a framework for the exploration of round-by-round
and ballot-by-ballot RLAs. The goal in designing R2B2 is two fold:
\begin{enumerate}
    \item Provide an elegant Python library which can be easily imported and used
    in any other code base.
    \item Provide an interactive set of tools which can be utilized `out-of-the-box'
    for experimenting with and learning about risk-limiting audits.
\end{enumerate}

@@

The high-level design of R2B2 is an object-oriented view of election audits.
The three main object classes, \code{Election}, \code{Contest}, and \code{Audit},
serve to group data into logically independent structures.

@@

The \code{Audit} contains information related to the audit parameters for a single contest, 
such as the risk limit, sampling method, and \code{Contest} to audit. It is important
to note the \code{Audit} is an Abstract Base Class upon which specific RLAs are built.
It only contains the parameters and attributes common to the RLAs of this paper and provides a set
of methods that can be called by any audit implementation. The functionality of
\code{Audit} can be divided into two basic groups: \textit{interactive}
and \textit{bulk}.\\
\\
The interactive implementation allows users to execute an audit step-by-step as it
might progress during a live election audit through the following:

@@

\subsection{Simulation Software}
As described above, our open source audit software library R2B2 has implementations of several ballot polling risk-limiting audits as well as a simulator, 
all written in Python.
For each of these audits, the software can compute the stopping condition for a given sample and estimates
of the next round size to achieve a desired stopping probability. 
For a given audit and random seed, the simulator draws random samples, with replacement, using a pseudorandom number generator, [need to check].
given the number of votes for each candidate, and the number of invalid votes, in the underlying election (these need not be chosen to be those announced).

When the number of candidates is more than two, the audit is carried out pairwise for each candidate pair, and votes for all other candidates are considered invalid votes. 
It is often useful to consider two underlying elections: one corresponding to a tie between the pair, and the other corresponding to the results as announced. These are the probability distributions represented
by the null and alternative hypotheses.

After drawing a simulated sample of ballots, the simulator evaluates the given audit's stopping condition for this sample.
If the audit stops, the simulation stops, and if the audit continues, the simulation draws another round. 
The abstract simulator class does not prescribe any one method for choosing round sizes. 
We implement several classes to support various round size choices: 
round sizes from an estimate to achieve a desired probability of stopping, 
predetermined round sizes, and pseudorandomly-generated round sizes.

\subsection{Testing}

The R2B2 (python) software is used to compute stopping conditions and next round estimates, it is intended for use by us and other researchers, and designed for this purpose. We have also independently implemented all the functionality in matlab (the two codebases are written by different individuals) and have extensively checked the results of the two codebases. Additionally, for use in regular election audits by election officials, we have written an add-on to the {\em Arlo} risk-limiting audit software, which has also been extensively checked against these two codebases.
